CRUSE to Safe Cycling in Ireland \\\large{An Open Source Tool to Support Active Travel}

### 2023-10-17 paper.qmd
Updates for submission

---
title: "CRUSE to Safe Cycling in Ireland"
subtitle: An Open Source Tool to Support Active Travel
bibliography: bibliography.bib
csl: apa.csl
editor:
  markdown:
    wrap: sentence
number-sections: true

# # Uncomment for draft versions:
format: 
  # html: default
  # docx: default
# # # Uncomment for formatted version
  elsevier-pdf:
    linestretch: 2
    keep-tex: true
    journal:
      name: European Transport Research Review
      formatting: preprint
      model: 3p
      cite-style: super
# # #   # pdf: default

@@

```{mermaid}
%%| fig-width: 100%
%%| fig-cap: Hypothetical user stories for the CRUSE Tool illustrating that it can be used in different ways by different user groups.
%%| label: fig-user-stories
graph LR
    A(Professional user) --> B[CRUSE landing page]
    B --> C[CRUSE national map]
    C --> D[CRUSE county map]
    D --> F[Full county map]
    D --> CS[County statistics]
    D --> Q[Quiet and fast route networks]
    D --> DD[Data downloads]
    DD --> EX{External tools}
    X(Non-professional user) --> Y[CRUSE landing page]
    Y --> Z[CRUSE national map]
    Z --> R[CRUSE county level results]
    Z --> E(Exploration)
    R --> E
    E --> COMS{Communication}
```

>>>>

---
title: "CRUSE to Safe Cycling in Ireland"
subtitle: An Open Source Tool to Support Active Travel
bibliography: bibliography.bib
csl: apa.csl
editor:
  markdown:
    wrap: sentence
number-sections: true
latex-clean: false
pdf-engine: pdflatex
knitr:
  opts_chunk:
    fig.path: images/
format: 
  # html: default
  # docx: default
# # # Uncomment for formatted version
  elsevier-pdf:
    linestretch: 2
    keep-tex: true
    journal:
      name: European Transport Research Review
      formatting: preprint
      model: 3p
      cite-style: super
# # #   # pdf: default

@@

```{r}
#| eval: false
#| echo: false
# ```{mermaid}
%%| eval: false
%%| fig-width: 100%
%%| fig-cap: Hypothetical user stories for the CRUSE Tool illustrating that it can be used in different ways by different user groups.
%%| label: fig-user-stories
graph LR
    A(Professional user) --> B[CRUSE landing page]
    B --> C[CRUSE national map]
    C --> D[CRUSE county map]
    D --> F[Full county map]
    D --> CS[County statistics]
    D --> Q[Quiet and fast route networks]
    D --> DD[Data downloads]
    DD --> EX{External tools}
    X(Non-professional user) --> Y[CRUSE landing page]
    Y --> Z[CRUSE national map]
    Z --> R[CRUSE county level results]
    Z --> E(Exploration)
    R --> E
    E --> COMS{Communication}
```

::: {#fig-user-stories}

![](images/mermaid-figure-1.png)

Hypothetical user stories for the CRUSE Tool illustrating that it can be used in different ways by different user groups.

:::

### 2023-10-17 paper.tex
Updates for submission

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, frame hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

\begin{figure}[H]

{\centering \includegraphics{paper_files/figure-latex/mermaid-figure-1.png}

>>>>

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, sharp corners, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable]}{\end{tcolorbox}}\fi

@@

\includegraphics{images/mermaid-figure-1.png}
